Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-05-03 CSM_poster/main.tex
test commit
more edits

@@

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

@@

\textcolor{dblue!70}{\ding{228}} iFixit's online question and answer forum, \textit{Answers}, features over 120,000 user-asked questions related specifically to device repair. Analysis of question response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how forum design can be improved.

\textcolor{dblue!70}{\ding{228}} \underline{Objective} Develop a Cox proportional hazards model to predict the survival probability (probability that a question remains unanswered beyond a certain time \textit{t}), of questions on the forum, with the goal of identifying variables significantly associated with response time.

@@

Data analyzed contained 7,760 questions posted from April 2017 to July 2017. 63.8\% received an answer. Shortest response time was 0.5 hours; longest was 2,159 hours (90 days). Figure 1 shows the distribution of response times for questions analyzed.

Original variables in the data include: device name and category, question title, text, tags, new user status, post date and answer date. Fourteen variables, capturing textual and user information, were derived from the data.

@@

%------------------------------------------------

\begin{figure}
\includegraphics[width=1\linewidth]{FIG1.pdf}
\caption{Distribution of response times}
\label{fig1}
\end{figure}

@@

\textcolor{dblue!70}{\ding{228}} \underline{Univariate Analysis} Used to identify which variables, as well as the optimal form of continuous variables (if transformations and restricted cubic splines should be applied), to include in the model.

\textcolor{dblue!70}{\ding{228}} \underline{Five Fold Cross-Validation} In each iteration, the model was built on the training set and used to predict hazard ratios on the test set.

\textcolor{dblue!70}{\ding{228}} \underline{Assessing Performance} Predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. Resulting Nagelkerke's $R^2$, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio (PLR) and p-value, were averaged over each iteration and assessed as performance indicators.

\textcolor{dblue!70}{\ding{228}} \underline{Final Model} The model was fit to the full data and proportional hazards assumption was assessed.

%----------------------------------------------------------------------------------------
%	MODEL BUILDING RESULTS
%----------------------------------------------------------------------------------------

\begin{block}{Model Building Results}

Univariate analysis determined that all categorical predictors should be retained. Table \ref{table:continuous} shows the form of continuous predictors included in the final model.

\renewcommand{\arraystretch}{1.2} % to increase the spacing between table rows
\begin{table}[!htbp]
\vspace{2ex}
\begin{tabular}{| l | c |}
    \hline
    \textbf{Predictor} & \textbf{Knots} \\
    \hline
    $\sqrt{\textnormal{average tag frequency}}$ & 0 \\
    $\log\left({\textnormal{average tag length} + 1}\right)$ & 4 \\
    $\sqrt{\textnormal{line breaks / text length}}$ & 5 \\
    $\sqrt{\textnormal{line breaks / text length}}$ & 3 \\
    $\log\left({\textnormal{text length}}\right)$ & 5 \\
    \hline
\end{tabular}
\caption{Form of continuous predictors included in the final model (knots indicates the number of knots included in restricted cubic splines}
\label{table:continuous}
\end{table}

Table \ref{table:1} displays the average performance metrics for models fit to test and training sets in cross-validation, as well as metrics for the model fit to the full data. Results for training, test, and the full data did not change significantly, indicating that the model was not over fit.

@@

%----------------------------------------------------------------------------------------
%	FINAL MODEL RESULTS
%----------------------------------------------------------------------------------------

\begin{block}{Final Model Results}

\underline{Final model statistics}

\underline{Significant Predictors} Device category, if the question was posted on a weekend or a weekday, whether or not the question's title contained at least one word considered frequently-used among unanswered questions, whether or not the question's title ends in a question mark.

\begin{table}[!htbp]
\vspace{3ex}
\begin{tabular}{|r|r|r|r|r|r|r|r|} % FIX THE R2 HERE 
  \hline
  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\ 
  \hline
  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
  \hline
\end{tabular}
\caption{Performance metrics (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)} 
\label{table:1}
\end{table}

Assessing the proportional hazards assumption indicated that several levels of the device categorization variable violated the assumption.

Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer. Table \ref{table:hr} contains interpretations of select hazard coefficients of the final model.

%----------------------------------------------------------------------------------------
%	SUGGESTIONS
%----------------------------------------------------------------------------------------

\begin{block}{Suggestions}

Results from this analysis lead to suggestions for changes in CQA design. Many users incorrectly specified device names and tags (e.g. a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One'').

@@

@@

\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
%----------------------------------------------------------------------------------------

@@

@@

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	HAZARD INTERPRETATIONS + SUGGESTIONS 
%----------------------------------------------------------------------------------------

\begin{block}

\renewcommand{\arraystretch}{1.15} % to increase the spacing between table rows
\begin{table}[!htbp]
\begin{tabular}{|p{26cm}|} 
  \hline
  The estimated hazard of receiving an answer is 154\% higher (95\% CI (132\%, 179\%)) for questions pertaining to Apple products than the hazard for questions about Android and Other phones, controlling for all other predictors. \\ \hline
  The estimated hazard of receiving an answer is 25\% lower (95\% CI (19\%, 29\%)) for questions with titles that contain at least one word considered to be frequently-used among unanswered questions, than the hazard for questions with titles that do not, controlling for all other predictors. \\ \hline
  The estimated hazard of receiving an answer for questions posted on a weekend is 13\% lower (95\% CI (7\%, 18\%)) than the hazard for questions posted on a weekday, controlling for all other predictors. \\ \hline
  \hline
\end{tabular}
\caption{Hazard coefficient interpretations} 
\label{table:hr}
\end{table}

It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some ways the CQA can be structured to potentially decrease response times. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions by restricting tags or devices users can include to a drop-down list. The CQA can also include more tips to guide users asking questions. Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

>>>>

\usepackage{multirow}
\usepackage{color,soul}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

\addtobeamertemplate{block end}{}{\vspace*{0.5ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

@@

\vspace{0.5ex}

iFixit's online question and answer forum, \textit{Answers}, features over 120,000 user-asked questions related specifically to device repair. Analysis of question response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how forum design can be improved.

\vspace{2ex}

\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Objective}} Develop a Cox proportional hazards model to predict the survival probability (probability that a question remains unanswered beyond a certain time \textit{t}), of questions on the forum, with the goal of identifying variables significantly associated with response time.

\vspace{0.5ex}

@@

\textcolor{dblue!70}{\ding{228}} 7,760 questions from April 2017 to July 2017.

\vspace{0.5ex}

\textcolor{dblue!70}{\ding{228}} 63.8\% received an answer

\vspace{0.5ex}

\textcolor{dblue!70}{\ding{228}} Shortest response time: 0.5 hours

\vspace{0.5ex}

\textcolor{dblue!70}{\ding{228}} Longest response time: 2,159 hours (90 days)

\begin{figure}
\vspace{2ex}
\includegraphics[width=1\linewidth]{FIG1.pdf}
\caption{Distribution of response times}
\label{fig1}
\end{figure}

Original variables include: device, question title, text, tags, new user status, post date and answer date. Fourteen variables, capturing textual and user information, were derived.

@@

\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Univariate Analysis}}

\vspace{0.5ex}

Used to identify which variables, as well as the optimal form of continuous variables (if transformations and restricted cubic splines should be applied), to include in the model.

\vspace{1ex}

\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Five Fold Cross-Validation}}

\vspace{0.5ex}

In each iteration, the model was built on the training set and used to predict hazard ratios on the test set.

\vspace{1ex}

\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Assess Performance}}

\vspace{0.5ex}

Predicted hazard ratios were entered into separate Cox models as the single predictor. Resulting $R^2$, concordance, Somers' \textit{Dxy}, partial likelihood ratio (PLR) and p-value, were averaged over each iteration and assessed.

\vspace{1ex}

\textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Final Model}}

\vspace{0.5ex}

The model was fit to the full data and proportional hazards assumption was assessed.

\vspace{1.5ex}

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

\begin{block}{Cross-Validation Results}

Table \ref{table:1} displays average performance metrics achieved in cross-validation, as well as for the model fit to the full data.

\begin{table}[!htbp]
\vspace{3ex}
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\
  \hline
  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\
  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\
  \hline
\end{tabular}
\caption{Performance metrics (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
\label{table:1}
\end{table}
\end{block}

\begin{block}{Final Model Statistics}

\vspace{0.5ex}

\vspace{0.5ex}

\vspace{0.5ex}

\textcolor{dblue!70}{\ding{228}} Several levels of the device categorization variable violated the proportional hazards assumption

@@

Controlling for all other predictors, the estimated hazard of receiving an answer is:

\vspace{1ex}

\textcolor{dblue!70}{\ding{228}} 154\% higher (95\% CI (132\%, 179\%)) for Apple products vs. Android/other phones

\vspace{0.75ex}

\textcolor{dblue!70}{\ding{228}} 13\% lower (95\% CI (7\%, 18\%)) for questions posted on the weekend vs. weekday

\vspace{1ex}

@@

\begin{block}{Forum Design Suggestions}

\textcolor{dblue!70}{\ding{228}} Rather than allowing users to enter any tag or device name, restrict options to a drop-down list

\vspace{0.5ex}

\textcolor{dblue!70}{\ding{228}} Include more tips to guide users when asking questions

@@

%----------------------------------------------------------------------------------------
\begin{block}{Final Model Coefficients}

\begin{table}[!htbp]
% \centering
\begin{tabular}{|L{10cm} L{17.5cm}|c|c|}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
                  & Camera & -0.32 (0.090) & \\ 
                  & Electronics & -0.01 (0.078)  & \\ 
                  & Game Console & 0.24 (0.083)  & \\ 
                  & Home & 0.34 (0.070) &  \\ 
                  & Other & -0.13 (0.056)  & \\ 
                  & PC & 0.28 (0.060) &  \\ 
                  & Tablet & -0.16 (0.081)  & \\ 
                  & Vehicle & 0.40 (0.069)  & \\
                  & Android/Other Phone (reference) & --- & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
\label{table:4}
\end{table}

@@

\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)

@@

% \begin{block}{Acknowledgements}
% 
% \small{\rmfamily{This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. We also thank iFixit for providing access to the CQA data.}} \\
% 
% \end{block}

@@

% \begin{column}{\sepwid}\end{column} % Empty spacer column

@@

% \setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

% \begin{block}{Acknowledgements}
% 
% \small{\rmfamily{This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. We also thank iFixit for providing access to the CQA data.}} \\
% 
% \end{block}
% 
% \end{column} % End of the third column
% 
\end{columns} % End of all the columns in the poster
